Mechanism of crystal-gel formation

### 2015-07-17 crystal-gel/crystal_gel_letter.tex
Letter layout Reorganise the figures according to what was decided with John.

%\documentclass[twocolumn,showpacs,amsmath,amssymb,pre,superscriptaddress]{revtex4}
%\documentclass[aps,prl,twocolumn,showpacs,amsmath,amssymb,superscriptaddress]{revtex4}
%\documentclass[a4paper,showpacs,aps,twocolumn,superscriptaddress]{revtex4}
\documentclass[a4paper,preprint,superscriptaddress]{revtex4}
\usepackage{graphicx}% Include figure files
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{comment}
%\usepackage{dcolumn}% Align table columns on decimal point
%\usepackage{bm}% bold math

@@

\begin{abstract}
{\bf 
Colloidal gels are usually formed by viscoelastic phase separation and its dynamical arrest by glass transition \cite{tanaka1999colloid,tanaka2000viscoelastic,foffi2002,lu2008gelation,zaccarelli2008gelation,testard2011}.
% Thus, the dynamical arrests of colloidal gels and glasses have been believed to originate from a dynamical transition to the same non-ergodic disordered glass state, i.e., vitrification. The only difference comes from the fact that the former is formed by densification induced by phase separation and thus is spatially heterogeneous whereas the latter is formed by homogeneous densification and thus spatially homogeneous.
With confocal measurements of a PMMA colloid and polymer mixture, we experimentally access the formation of \emph{crystal-gels}, a novel arrested phase in which the dense branches of a gel are replaced by crystal aggregates~\cite{fortini2008crystallization,perez2011pathways,sabin2012}. 
For the first time we are able to observe the formation mechanism of crystal-gels at a single-particle level, giving experimental access to the elementary process of this novel route to gelation, in which phase separation is not arrested by slow dynamics but by crystallization.
The formation of the crystal gel  involves a new kinetic pathway, in which crystal seeds form inside the liquid branches of the spinodal aggregate, but then grow by direct condensation from the gas phase.
We argue that crystal gels can form as the result of the gas-liquid phase separation of crystallizable components, such as monoatomic and molecular systems, whose dynamics is slow enough to induce viscoelastic phase separation, but fast enough to prevent immediate vitrification.
% , which is necessary to form a network structure of a minority liquid phase in a majority gas phase, and at the same time fast enough to prevent immediate vitrification.
For example, our experiment provides a colloidal model of the Bergeron process (or ``cold-rain process''), which regulates ice crystal growth that occurs in mixed phase clouds containing a mixture of supercooled water and ice~\cite{glickman2000glossary}.
}
\end{abstract}

@@

@@

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=8cm,clip]{oldfig/fig1a}
  \includegraphics[width=8cm]{oldfig/fig1b}
 % csd_beforegrl.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
 \caption{{\bf Characterisation of gels formed by phase separation.} {\bf a,} 
 Cluster size distribution for all state points at percolation, where $s$ is the size of the cluster. Different power-laws are represented with dashed lines. 
{\bf b,} Radius of gyration ($R_g$) for clusters at the gel point.}
 \label{fig:gel}
\end{figure}

\begin{figure}[!t]
 \centering
 \includegraphics[width=8cm]{oldfig/fig2a}
  \includegraphics[width=8cm]{oldfig/fig2b}
  \includegraphics[width=8cm]{oldfig/fig2c}
 % figure_restructuring.eps: 990x765 pixel, 300dpi, 8.38x6.48 cm, bb=0 -1 1453 480
 \caption{{\bf Stress-induced ageing.} {\bf a,} Fraction of liquid and gas particles as a function of time during phase separation for state points
 $\phi=0.10$, $c_p=0.82$ (continuous lines) and $c_p=1.36$ (dashed lines). The two vertical (green) lines are located at time $t=600\,s$ and $t=700\,s$
 respectively. {\bf b,} Average number of bond breaking events
 per particle for the state point $\phi=0.10$, $c_p=1.36$. The fraction of liquid particles for the same state point
 is also depicted for clarity. The two vertical (green) lines are located at time $t=600\,s$ and $t=700\,s$
 respectively.
{\bf c,} Time evolution of the structure factor, $S(q)$, for the state point $\phi=0.10$ and $c_p=0.82$.}
 \label{fig:stress}
\end{figure}

\begin{figure}[!t]
 \centering
 \includegraphics[width=8cm]{oldfig/fig3a}
 \includegraphics[width=8cm]{oldfig/fig3b}
 \includegraphics[width=8cm]{oldfig/fig3c}
 \includegraphics[width=8cm]{oldfig/fig3d}
 % crystal_size.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
 \caption{{\bf Two types of arrest mechanism leading to gel formation.} {\bf a,} Time evolution of the average size of the crystals (black line) and the number of crystals (red line) for the state point $\phi=0.25$ and $c_p=0.38$. {\bf b,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle.
 Different lines represent the different state points. {\bf c,} Structure factors for the late stages of the gelation process. Calculation of the structure factor is done with the Hanning window function,  to minimize boundary effects. {\bf d,} Radius of gyration of crystalline nuclei at the late stages of gelation for the state point $\phi=0.25$ and $c_p=0.38$.} 
 \label{fig:crystals}
\end{figure}

\begin{figure}[!t]
 \centering
 \includegraphics[width=16cm]{oldfig/fig4a}
 \includegraphics[width=8cm]{oldfig/fig4b}
 \includegraphics[width=8cm]{oldfig/fig4c}
 % snapshots.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=0 -1 2256 735
 \caption{
{\bf Crystal gel formation.} 
{\bf a,} Snapshots of configurations at $\phi=0.25$ and $c_p=0.38$, for t=4856 (left), 12956 (center), 27956 (right). Particles are colored according to their phase. Green: HCP; Red: FCC; blue: BCC; white: liquid or gas. 
 {\bf b,} Fraction of particles for each phase (between bcc, hcp, fcc, surface, liquid or gas) at $\phi=0.25$ and $c_p=0.38$.
 Crystalline phases are detected through bond orientational analysis~\cite{russo2012microscopic}; surface particles are particles
 with at least two crystalline neighbours; liquid particles have at least 4 neighbours; gas particles are particles with less than 4
 nearest neighbours.
{\bf c,} Transition probabilities for the same process as in {\bf b}. Crystal includes all crystalline phases (bcc, hcp, fcc) and surface particles.}
 \label{fig:transitions}
\end{figure}

>>>>

\documentclass[twocolumn,superscriptaddress,showpacs,preprintnumbers,
amsmath,amssymb,prl]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}% Include figure files
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{comment}
%\usepackage{dcolumn}% Align table columns on decimal point
%\usepackage{bm}% bold math

@@

\begin{abstract}
{
Colloidal gels are usually formed by viscoelastic phase separation and its dynamical arrest by glass transition \cite{tanaka1999colloid,tanaka2000viscoelastic,foffi2002,lu2008gelation,zaccarelli2008gelation,testard2011}.
% Thus, the dynamical arrests of colloidal gels and glasses have been believed to originate from a dynamical transition to the same non-ergodic disordered glass state, i.e., vitrification. The only difference comes from the fact that the former is formed by densification induced by phase separation and thus is spatially heterogeneous whereas the latter is formed by homogeneous densification and thus spatially homogeneous.
With confocal measurements of a PMMA colloid and polymer mixture, we experimentally access the formation of \emph{crystal-gels}, a novel arrested phase in which the dense branches of a gel are replaced by crystal aggregates~\cite{fortini2008crystallization,perez2011pathways,sabin2012}. 
For the first time we are able to observe the formation mechanism of crystal-gels at a single-particle level, giving experimental access to the elementary process of this novel route to gelation, in which phase separation is not arrested by slow dynamics but by crystallization.
The formation of the crystal gel  involves a new kinetic pathway, in which crystal seeds form inside the liquid branches of the spinodal aggregate, but then grow by direct condensation from the gas phase.
We argue that crystal gels can form as the result of the gas-liquid phase separation of crystallizable components, such as monoatomic and molecular systems, whose dynamics is slow enough to induce viscoelastic phase separation, but fast enough to prevent immediate vitrification.
% , which is necessary to form a network structure of a minority liquid phase in a majority gas phase, and at the same time fast enough to prevent immediate vitrification.
For example, our experiment provides a colloidal model of the Bergeron process (or ``cold-rain process''), which regulates ice crystal growth that occurs in mixed phase clouds containing a mixture of supercooled water and ice~\cite{glickman2000glossary}.
}
\end{abstract}

@@

\begin{figure}
 \centering
 \framebox{Phase diagram\hfill}
 \includegraphics[width=8cm]{oldfig/fig3b}
 \includegraphics[width=8cm]{oldfig/fig3c}
 % crystal_size.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
 \caption{{\bf Two types of arrest mechanism leading to gel formation.} \textbf{a,} Phase diagram \textbf{b,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle.
 Different lines represent the different state points. {\bf c,} Structure factors for the late stages of the gelation process.} 
 \label{fig:statepoints}
\end{figure}

\begin{figure}[!t]
 \centering
 \includegraphics[width=8cm]{oldfig/fig3a}
 \includegraphics[width=8cm]{oldfig/fig3d}
 % crystal_size.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
 \caption{{\bf Characterisation of the crystal-gel.} {\bf a,} Time evolution of the average size of the crystals (black line) and the number of crystals (red line) for the state point $\phi=0.25$ and $c_p=0.38$. {\bf d,} Radius of gyration of crystalline nuclei at the late stages of gelation for the same state point.} 
 \label{fig:crystals}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[width=16cm]{oldfig/fig4a}
 \includegraphics[width=8cm]{oldfig/fig4b}
 \includegraphics[width=8cm]{oldfig/fig4c}
 % snapshots.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=0 -1 2256 735
 \caption{
{\bf Crystal gel formation.} 
\textbf{a,} Snapshots of configurations at $\phi=0.25$ and $c_p=0.38$, for t=4856 (left), 12956 (center), 27956 (right). Particles are colored according to their phase. Green: HCP; Red: FCC; blue: BCC; white: liquid or gas. 
 \textbf{b,} Fraction of particles for each phase (between bcc, hcp, fcc, surface, liquid or gas) at $\phi=0.25$ and $c_p=0.38$.
 Crystalline phases are detected through bond orientational analysis~\cite{russo2012microscopic}; surface particles are particles
 with at least two crystalline neighbours; liquid particles have at least 4 neighbours; gas particles are particles with less than 4
 nearest neighbours.
\textbf{c,} Transition probabilities for the same process as in \textbf{b}. Crystal includes all crystalline phases (bcc, hcp, fcc) and surface particles.}
 \label{fig:transitions}
\end{figure*}

@@
